\section{Sample Job Description}

\begin{tcolorbox}[colback=boxbackground,colframe=boxframe,sharp corners]

\noindent \textbf{Overview}\\
We are one of the world’s leading financial institutions ... and risk management products and services.

\noindent \textbf{Process Overview}\\
Build and evolve a consistent Authorized Data Source within Consumer \& Small Business Bank (CSBB) ... both the strategic and tactical analytics needs of the Consumer Bank.

\noindent \textbf{Job Description}\\
Hadoop developer for multiple initiatives. Develop Big Data Strategy and Roadmap for the Enterprise. Experience in Capacity Planning, Cluster Designing and Deployment. Benchmark systems, analyze system bottlenecks, and propose solutions to eliminate them. Develop highly scalable and extensible Big Data platform, which enables collection, storage, modeling, and analysis of massive data sets from numerous channels. Continuously evaluate new technologies, innovate and deliver solution for business-critical applications.

\noindent \textbf{Responsibilities}\\
Assists the team with the design of the architect layer to ensure re-usable metrics and attributes within the reporting layer. Responsible for creating and maintaining necessary documentation (MDR) to ensure audit readiness where necessary. Prototype improvement ideas. Work effectively with the global team. Expected to play technical leadership as an individual contributor. Articulate challenges, propose and drive solutions ...

\noindent \textbf{Mandatory Skills}\\
Extensive knowledge of Hadoop stack and storage technologies HDFS, MapReduce, Yarn, HIVE, sqoop, Impala, spark, flume, kafka and oozie. Extensive Knowledge on Bigdata Enterprise architecture (Cloudera preferred). Experience in No SQL Technologies (Cassandra, Hbase).

\noindent \textbf{Desired Skills}\\
Experience in Real time streaming (Kafka). Experience with Big Data Analytics \& Business Intelligence and Industry standard tools integrated with Hadoop ecosystem. (R , Python ). Visual Analytics Tools knowledge (Tableau ). Data Integration, Data Security on Hadoop ecosystem. (Kerberos ). Awareness or experience with Data Lake with Cloudera ecosystem.
\end{tcolorbox} 

\captionof{figure}{This is a more detailed version of a sample vacancy posting with only information about the firm and the relevant sub-division redacted.}


